%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experiences \& Academic Projects}

% Advices:
% Take responsability for what you have done avoid passive form ("Implementation of" instead of "Implemented")
% 

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Constrained Inverse Reinforcement Learning: challenges and solutions of a real world implementation} % Job title
    {Master's Thesis - Sycamore Lab} % Organization
    {Ecublens VD, CH} % Location
    {March 2023 - Jul. 2023} % Date(s)
    {
    Grade : 5.5/6 - Supervisor : Andreas Schlaginhaufen - Professor : Maryam Kamgarpour\vspace{1.5em}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Hardware}: Jetbots, Jetson Nanos, Optitrack tracking system 
        \item \textbf{Software}: Ubuntu, Python, ROS2, PyTorch, Gym
        \item Implementation and design of an entire Reinforcement Learning (RL) framework of 6000+ lines of clean, tested and commented Python code.
        \item Design of two algorithms based on state of the art methods (DQN, iQ-Learn, ...) to perform CIRL.
        % \item Extensively studied RL theory (Sutton \& Barto, DeepMind Lectures) and implementation.
        % \item Integration of the developed CIRL algorithms with the ROS2 framework I previously created for the lab.
        % \item Writing and extending the existing documentation.
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {R\&D intern} % Job title
    {Insolight SA} % Organization
    {Renens VD, CH} % Location
    {Sept. 2022 - March 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Hardware}: Raspberry Pi, Modbus sensors, Electrical motors, PV modules
        \item \textbf{Software}: Python \& C++
        \item Implementation of a failure detection algorithm for extreme meteorological conditions using Kalman filtering to fuse the sensors measurements.
        % \item Creation of a testbed for the estimation of the panels' diffusion coefficient using computer vision and machine learning.
        % \item Sensor setup and installation using the Modbus protocol.
        \item Implementation of the calibration and sun tracking algorithm for the Hiperion project, using C++.
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Semester Project \& Summer internship} % Job title
    {Sycamore Lab} % Organization
    {Ecublens VD, CH} % Location
    {Feb. 2022 - Sept. 2022} % Date(s)
    {
    Grade : 5.5/6 - Supervisor : Dr. Tony A. Wood - Professor : Maryam Kamgarpour\vspace{1.5em}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Hardware}: Jetbots, Jetson Nanos, Optitrack tracking system}
        \item {\textbf{Software}: Ubuntu, shell, Python, ROS \& ROS2, Acados}
        \item Development of a ROS2 framework enabling multi-agent coordination and control, consisting of 10,000+ lines of documented and well-structured code, which remains in active use.
        % \item Provide comprehensive code documentation, enabling seamless continuation after my involvement.
        % \item Configured firmware to ensure compatibility between JetPack SDK, ROS2 Foxy, and the Python libraries.
        % \item Streamlined robot boot and ROS node launching processes through automated tasks using shell scripting and boot services.
        \item Implementation of control and path planning methods (MPC, cCAPT, Pure Pursuit, LQR).
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
